\documentclass[a4paper,10pt]{article}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{parskip}
\usepackage[margin=0.75in]{geometry}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\renewcommand{\maketitle}{
    \hspace{-1em}\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{\LARGE Gal Cesana} & \textbf{Phone:} 052-4085511 \\
        \textbf{Email:} galcesana8@gmail.com & \textbf{GitHub:}  \\
        \textbf{LinkedIn:}  & \textbf{Location:} Tel Aviv, Israel \\
    \end{tabular*}
    \vspace{1em}
}

\begin{document}

\maketitle

% Summary Section
\section*{Summary}
Highly motivated and skilled computer science student seeking a challenging R\&D position in software development. Proven ability to leverage programming, machine learning, and data analysis skills to contribute to impactful projects. Expertise in Python, C++, TensorFlow, and PyTorch, coupled with experience in developing data annotation tools and working in a real-world R\&D environment. Eager to learn and contribute to innovative solutions. 

% Skills Section
\section*{Technical Skills}
\begin{itemize}[noitemsep,nolistsep]
    \item \textbf{Languages:} Python, C, C++, Java, PostgreSQL
    \item \textbf{Machine Learning and Data Analysis Libraries:} TensorFlow, PyTorch, Pandas, NumPy
    \item \textbf{Tools:} Git, Linux, Data Annotation Tools (developed in Python)
\end{itemize}

% Experience Section
\section*{Professional Experience}
\textbf{Data Annotator} \hfill SAIPS (A Ford Motor Company Subsidiary), Tel Aviv, Israel \\
\textit{Dec 2021 -- Oct 2022}
\begin{itemize}[noitemsep,nolistsep]
    \item Developed and utilized data annotation tools in collaboration with developers to label data, enabling the training of neural network models for autonomous vehicle systems.
    \item Gained hands-on experience with Python, data processing, and annotation for machine learning applications in a real-world R\&D environment.
    \item Contributed to the improvement of data quality and efficiency in a fast-paced research setting.
\end{itemize}

\textbf{HR Officer (Captain)} \hfill Israel Defense Forces (IDF) \\
\textit{Jul 2018 -- May 2021}
\begin{itemize}[noitemsep,nolistsep]
    \item Led the HR department for a unit of 500 personnel, managing all HR planning, data handling, and administrative tasks.
    \item Supervised a team of 12, developing strong teamwork and leadership skills in a fast-paced and high-responsibility setting.
    \item Demonstrated ability to effectively manage and organize large amounts of information and personnel, ensuring efficient operations. 
\end{itemize}

% Education Section
\section*{Education}
\textbf{B.Sc. in Computer Science} \hfill The Hebrew University of Jerusalem \\
\textit{Expected Graduation: 2026} 

% Projects Section
\section*{Projects}
\textbf{Machine Learning Projects} \\
\begin{itemize}[noitemsep,nolistsep]
    \item Developed and implemented machine learning models using TensorFlow, PyTorch, Pandas, and NumPy for various applications, including image classification and data analysis.
    \item Gained practical experience in data preprocessing, feature engineering, and model training and evaluation techniques. 
    \item Enhanced understanding of the application of machine learning algorithms to solve real-world problems.
\end{itemize}

% Additional Section
\section*{Relevant Coursework}
\begin{itemize}[noitemsep,nolistsep]
    \item Algorithms
    \item Data Structures
    \item Operating Systems
    \item Data Bases
    \item OOP
    \item Network Systems
    \item Software Engineering
    \item Introduction to Natural Language Processing
    \item Machine Learning Methods
    \item Introduction to Machine Learning
\end{itemize}

\end{document}